### 2013-08-23 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
cleaning up some whitespace to reduce the length
spell check for spn chapter edits
spell check for nonlinear chapter

\begin{figure}[t!]
  \begin{center}
    \scalebox{0.6}{ \input{chapters/parallel_mc/msod_construction.pdftex_t} }
  \end{center}
  \caption{\textbf{MSOD construction for 4 sets with overlap.}
    \textit{The linear system is used to construct the Monte Carlo
      transport domain on the primary set. The Monte Carlo data
      structures are then broadcast among the blocks to all sets in
      the system.}}
  \label{fig:msod_construction}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \scalebox{0.6}{ \input{chapters/parallel_mc/msod_tally.pdftex_t} }
  \end{center}
  \caption{\textbf{MSOD tally reduction over blocks.} \textit{The
      tally computed independently in each set is reduced across the
      blocks to the primary set. The linear system vector is updated
      on the primary set. In this example the tally vector in the
      block containing upper-left subdomains is combined. Identical
      reduction operations occur for all other blocks
      simultaneously.}}
  \label{fig:msod_tally_reduction}
\end{figure}

@@

In this chapter we have developed a domain-decomposed parallel
algorithm for Monte Carlo Synthetic Acceleration and explored the
qualities of the algorithm through parallel scaling studies. The
following are the significant observations and findings.

>>>>

\begin{figure}[t!]
  \begin{center}
    \scalebox{0.55}{ \input{chapters/parallel_mc/msod_construction.pdftex_t} }
  \end{center}
  \caption{\textbf{MSOD construction for 4 sets with overlap.}
    \textit{The linear system is used to construct the Monte Carlo
      transport domain on the primary set. The Monte Carlo data
      structures are then broadcast among the blocks to all sets in
      the system.}}
  \label{fig:msod_construction}
\end{figure}

@@

\begin{figure}[t!]
  \begin{center}
    \scalebox{0.55}{ \input{chapters/parallel_mc/msod_tally.pdftex_t} }
  \end{center}
  \caption{\textbf{MSOD tally reduction over blocks.} \textit{The
      tally computed independently in each set is reduced across the
      blocks to the primary set. The linear system vector is updated
      on the primary set. In this example the tally vector in the
      block containing upper-left subdomains is combined. Identical
      reduction operations occur for all other blocks
      simultaneously.}}
  \label{fig:msod_tally_reduction}
\end{figure}

@@

In this chapter we have developed a domain-decomposed parallel
algorithm for Monte Carlo Synthetic Acceleration and explored the
qualities of the algorithm through parallel scaling studies. The
following are the significant observations, findings, and
contributions.
